Ornaments as indicators of social changes and cultural practices in northeast Taiwan before and after European colonial period

### 2019-12-07 analysis/paper/paper.Rmd
edited the text and revised the table

```{r C14-table-data}
kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))
table_kw_dates <-
  kw_dates %>% 
  select(-se, -rce)

@@

Point pattern analysis can assess whether the distribution of artefacts represents hotspots produced by non-random processes [@Bevan2016; @Ducke2015], such as concentrations of ornaments resulting from social inequality stimulated by a colonial presence. To prepare the ornament location data for point pattern analysis, I assigned each ornament to a random coordinate pair located in 4 x 4 m square it was recovered from (ornaments lack individual point provenance). The next step was to divide the ornaments into three time periods. Finally I computed the kernel densities for each time period for comparison. Kernel density estimations (KDE) compute the probability of the density of ornaments across space by creating a continuous, smooth density surface across space. Here I use KDE to visualize core areas of ornaments and surrounding neighbourhoods [@Bonnier2019; @Cortegoso2016]. Density values of artefacts per square meter were calculated for each cell.

>>>>

```{r C14-table-data}
kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))
table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  mutate(Period = as.factor(Period)) %>% 
  mutate(Period = factor(Period,
                       level = c("pre-European", 
                                 "European", 
                                 "post-European"))) %>% 
  arrange(Period) %>% 
  select("Pit-Layer", "Depth related to sea level (cm)", Period, "Date BP", "Calibrated date", "Details")

@@

Point pattern analysis can assess whether the distribution of artefacts represents hotspots produced by non-random processes [@Bevan2016; @Ducke2015], such as concentrations of ornaments resulting from social inequality stimulated by a colonial presence. To prepare the ornament location data for point pattern analysis, I assigned each ornament to a random coordinate pair located in 4 x 4 m square it was recovered from (ornaments lack individual point provenance). The next step was to divide the ornaments into three time periods. All squares in the sampling area were occupied during all phases of habitation based on the continuous presence of archaeological materials across over the strata representing a time span of 600 years. Although the quantity of locally made pottery declines in the later period with the growth of the Chinese porcelains, the general density of the artifacts present consistent thoughout all three phases.

Finally I computed the kernel densities for each time period for comparison. Kernel density estimations (KDE) compute the probability of the density of ornaments across space by creating a continuous, smooth density surface across space. Here I use KDE to visualize core areas of ornaments and surrounding neighbourhoods [@Bonnier2019; @Cortegoso2016]. Density values of artefacts per square meter were calculated for each cell.
